The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-04-14 paper.tex
add info on l-curves and how to compute the psf

@@

@@

Tikhonov regularization requires the observer to pick the value of $\epsilon$. If $\epsilon$ is too
large then too much importance is placed on minimizing the norm of the solution and the
least-squares residuals will suffer. However if $\epsilon$ is too small then the problem will be
poorly regularized and the resulting sky map may not represent the true sky.

A tool that can be used to address this problem is the L-Curve.

@@

>>>>

\subsection{$m$-Mode Analysis Imaging}

@@

\subsubsection{The Moore-Penrose Pseudoinverse}

\subsubsection{Tikhonov Regularization}

@@

\subsubsection{L-Curves}

Tikhonov regularization requires the observer to pick the value of $\epsilon$. If $\epsilon$ is too
large then too much importance is placed on minimizing the norm of the solution and the
least-squares residuals will suffer. However if $\epsilon$ is too small then the problem will be
poorly regularized and the resulting sky map may not represent the true sky. Picking the value of
$\epsilon$ therefore requires understanding the trade-off between the two norms.

This trade-off can be analyzed quantitatively by trialing several values of $\epsilon$ and computing
$\|\b v - \b B\b a\|^2$ and $\|\b a\|^2$ for each trial. An example is shown in Figure \todo{create
a figure}. The shape of this curve has a characteristic L-shape, and as a result this type of plot
is called an L-curve \todo{reference}. The ideal value of $\epsilon$ lies near the turning point of
the plot. At this point a small decrease in $\epsilon$ will lead to an undesired rapid increase in
$\|\b a\|^2$, and a small increase in $\epsilon$ will lead to an undesired rapid increase in $\|\b v
- \b B\b a\|^2$.

In practice, the L-curve should be used as a guide to estimate a reasonable value of $\epsilon$.
However better results can often be obtained by tuning the value of $\epsilon$. For instance
increasing the value of $\epsilon$ can improve the noise properties of the map by down-weighting
noisy modes. Decreasing the value of $\epsilon$ can improve the resolution in the map by
up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
imaging where robust weighting schemes can be tuned to similar effect.

@@

While $m$-mode analysis imaging automatically deconvolves large angular scales, point sources do not
get deconvolved by the imaging process. This is a limitation of the set of basis functions we have
chosen to represent the sky -- the spherical harmonics. Point sources carry power to large values of
$l$, but the regularization will eventually begin to downweight spherical harmonics with $l$ larger
than what the interferometer is sensitive to. This consequence of this is that point sources will
appear in the maps with some characteristic point spread function. This point spread function may be
computed with
\begin{equation}
    \b a_\text{PSF}(\theta, \phi)
        = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
\end{equation}
where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
the point spread function at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta,
\phi)$ is the vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given
by
\begin{equation}
    a_{lm, \text{PS}}(\theta, \phi) = Y_{lm}^*(\theta, \phi)\,.
\end{equation}

\todo{include a few images of the computed PSF for my maps}

\todo{describe how we incorporate this into major and minor iterations}
